Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-28 fmics/paper.tex
some tweaks to a table in section 3

\usepackage{times,graphicx,epsfig,boxedminipage,url,xspace,array,amsmath}

@@

As shown in Table~\ref{}, by cascading 6 slices, it is enough to reach the 100 seconds upper integration limit requested by the specifications.

@@

\begin{figure}[t]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c}{Range} &\multicolumn{2}{|c|}{Refreshing} & & \\\cline{1-4}
40 us steps & ms & 40 us steps  & ms & slice No & running sum \\\hline\hline
1 & 0.04 & 1 & 0.04 & & RS0 \\\hline
2 & 0.08 & 1 & 0.04 & & RS1 \\\hline
8 & 0.32 & 1 & 0.04 & slice 1 & RS2 \\\hline
16 & 0.64 & 1 & 0.04 & & RS3 \\\hline
64 & 2.56 & 2 & 0.08 & slice 2 & RS4 \\\hline
256 & 10.24 & 2 & 0.08 & & RS5 \\\hline
2048 & 81.92 & 64 & 2.56 &slice  3 & RS6 \\\hline
16384 & 655.36 & 64 & 2.56 &slice 3 & RS7 \\\hline
32768 &1310.72 & 2048 & 81.92 & slice 4 & RS8 \\\hline
131072 & 5242.88 & 2048 & 81.92 & slice 4 & RS9 \\\hline
524288 & 2097.52 & 16384 & 655.36 & slice 5 &RS10 \\\hline
2097152 & 83886.08 & 16384 & 655.36 & slice 5 & RS11 \\\hline

\end{tabular}
\vspace{0.04in}
\label{fig:example-bakery}
\caption{}
\end{figure}

>>>>

\usepackage{times,graphicx,epsfig,boxedminipage,url,xspace,array,amsmath,textcomp}

@@

As shown in Table~\ref{fig:example-bakery}, cascading 6 slices is enough to reach the 100 second upper integration limit requested by the specifications.

@@

\begin{table}[t]
\centering
\begin{tabular}{|r|r|r|r|c|l|}
\hline
\multicolumn{2}{|c}{Range} &\multicolumn{2}{|c|}{Refreshing} & & \\\cline{1-4}
40 {\textmu}s steps & ms & 40 {\textmu}s steps  & ms & slice & running sum \\\hline\hline
1 & 0.04 & 1 & 0.04 & & RS0 \\\hline
2 & 0.08 & 1 & 0.04 & & RS1 \\\hline
8 & 0.32 & 1 & 0.04 & slice 1 & RS2 \\\hline
16 & 0.64 & 1 & 0.04 & & RS3 \\\hline
64 & 2.56 & 2 & 0.08 & slice 2 & RS4 \\\hline
256 & 10.24 & 2 & 0.08 & & RS5 \\\hline
2048 & 81.92 & 64 & 2.56 &slice  3 & RS6 \\\hline
16384 & 655.36 & 64 & 2.56 &slice 3 & RS7 \\\hline
32768 &1310.72 & 2048 & 81.92 & slice 4 & RS8 \\\hline
131072 & 5242.88 & 2048 & 81.92 & slice 4 & RS9 \\\hline
524288 & 2097.52 & 16384 & 655.36 & slice 5 &RS10 \\\hline
2097152 & 83886.08 & 16384 & 655.36 & slice 5 & RS11 \\\hline
\end{tabular}
\vspace{0.04in}
\caption{{\bf<missing caption>}
\label{fig:example-bakery}}
\end{table}
